Robertson and Cao Project

### 2024-02-20 products/manuscript/Manuscript.qmd
Kelly's Change- Updated some files
Deleted some unnecessary files, updated the create_data_frame file to save data set into rds file, move files to appropriate location

The data will then be converted the data frame to a readable and downloadable .csv file for further analysis
```{r, echo=FALSE, message=FALSE}
output_file<-"NIS_Teen_Data_2022.csv"
write.csv(data, file = output_file, row.names = FALSE)
```

>>>>

The data will then be converted the data frame to a readable and downloadable .csv file for further analysis
```{r, echo=FALSE, message=FALSE}
output_file<-"NIS_Teen_Data_2022.csv"
write.csv(data, file = output_file, row.names = FALSE)

#A .rds file of it is saved in the following folder
saveRDS(data, file = "./data/processed-data/processeddata.rds")
```
